---
title: "Untitled"
author: "Shankar K Shakya"
date: "January 27, 2017"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 12, echo = F, warning = F, message = F, verbose = F)


```

### Phytophthora infestans diversity in three states of Mexico. Locus D13 is removed because of high percentage of missing values and all analysis is done on diploid genotypes. Data from Wang et.al 2016 (Mch, Toluca and Tlaxcala) is added to our new dataset of 2015/16.

```{r, echo=FALSE}

rm(list = ls())
library(poppr, quietly = TRUE)

P.inf <- read.genalex("MX_pop.csv", ploidy = 4)

source("multiploid2diploid.R")
diploid_pinf <- multiploid2diploid(P.inf, to = 2)
info_table(diploid_pinf, type = "missing", plot = T)

library(ggplot2)
missing_plot <- last_plot()
missing_plot + theme(text = element_text(size = rel(5))) + theme(legend.position = "none") + 
  theme(plot.title = element_text(size = 30)) + theme(axis.text.x = element_text(size = 15))



diploid_pinf <- missingno(diploid_pinf, type = "loci", cutoff = 0.07)

splitStrata(diploid_pinf) <- ~Region/Year
setPop(diploid_pinf) <- ~Region

# Corrected simpson diversity index
uSimp <- function(x){
  lambda <- vegan::diversity(x, "simpson")
  x <- drop(as.matrix(x))
  if (length(dim(x)) > 1){
    N <- rowSums(x)
  } else {
    N <- sum(x)
  }
  return((N/(N-1))*lambda)
}


unbiased <- poppr(diploid_pinf, uSimp = uSimp)

unbiased <- unbiased[, c(1,2,3,4,9,10,11)]
colnames(unbiased) <- c("Region", "N", "MLG", "eMLG", "E5", "Corrected lambda", "Hexp")
unbiased <- unbiased[c(6,1,4,3,2,5), ]
rownames(unbiased) <- NULL

#write.csv(unbiased, "diversity.csv"")


library(knitr)
kable(unbiased, digits = 2,
      align = c("c"),
      caption = "Table xx. P. infestans sampling locations in Mexico and population statistics for diploid genotypes based on eleven SSR loci.  Total number of samples (N), observed multilocus genotype (MLG), expected multilocus genotype (eMLG), eveness (E5), corrrected Simpson's diversity index (Corrected lambda) and expected heterozygosity (Hexp)")


# library(ggplot2)
# 
# unbiased$Region <- factor(unbiased$Region, levels = unbiased$Region)
# 
# ggplot(data = unbiased, aes(x = Region, y = Hexp, fill = Region)) + geom_bar(stat = "identity")

```


##TEST FOR LINKAGE DISEQUILIBRIUM

```{r}


ia_Pinf <- poppr(diploid_pinf, clonecorrect = TRUE, strata = ~Region, sample = 999, quiet = TRUE)
ia_Pinf <- ia_Pinf[,c(1:3,13:14)]  
colnames(ia_Pinf) <- c("Region", "N", "MLG", "rbarD", "P-value")


p <- last_plot()
p
p$data

str(p)

ggsave(p, filename = "ia.png", width = 7, height = 6)

```


##Hardy-Weinberg equilibrium

```{r}

library(pegas)

diploid_pinf_cc <- clonecorrect(diploid_pinf)
hwe_per_pop <- seppop(diploid_pinf_cc) %>% lapply(hw.test, B = 1000)
per_pop_mat <- sapply(hwe_per_pop, "[", i = TRUE, j = 3)
alpha <- 0.05
per_pop_mat[per_pop_mat > alpha] <- 1


library(lattice)

hwe_plot <- levelplot(per_pop_mat, xlab = "Locus", ylab = "Population")
hwe_plot

num_loci_hwe <- per_pop_mat
num_loci_hwe[num_loci_hwe != 1] <- 0
num_loci_hwe <- colSums(num_loci_hwe)


ia_Pinf <- ia_Pinf[-7, ]
ia_Pinf <- cbind(ia_Pinf, num_loci_hwe) 
ia_Pinf <- ia_Pinf[c(6,1,4,3,2,5), ]
rownames(ia_Pinf) <- NULL
colnames(ia_Pinf[6]) <- "Number of loci under HWE"
 
kable(ia_Pinf, 
      digits = 2,
      align = c("c"),
      caption = "Table xxx. Standardized index of association (rbarD), a measure of linkage disequilibrium among loci, and number of loci under Hardy-Weinberg equilibrium on diploid clone corrected dataset of P.infestans based on eleven SSR markers")



```



```{r, eval=FALSE, include=FALSE}
## STRUCTURE

library(strataG)
Sys.setenv(PATH = paste("C:/Program Files (x86)/Structure2.3.4/bin", Sys.getenv("PATH"), sep = ";"))
Sys.setenv(PATH = paste("C:/Users/Shankar/Downloads/CLUMPP_Windows.1.1.2/", Sys.getenv("PATH"), sep = ";"))

gen2gtype <- function (x) {
  
  gen.mat <- genind2df(x, usepop = TRUE, oneColPerAll = TRUE)
  strata <- x@strata
  rownames(strata) <- rownames(gen.mat)
  x@strata <- strata
  gen.mat[gen.mat == "NA"] <- NA
  has.pop <- !is.null(x@pop)
  df2gtypes(x = gen.mat, ploidy = x@ploidy[1], id.col = NULL, 
            strata.col = if (has.pop) 
              1
            else NULL, loc.col = if (has.pop) 
              2
            else 1, 
            schemes = x@strata,  other = other(x))
}

diploid_pinf.g <- gen2gtype(diploid_pinf)

sr <- structureRun(diploid_pinf.g, k.range  = 1:6, burnin = 20000, num.k.rep = 15, noadmix = F, numreps = 100000)

#save(sr, file = "dip")

str_data <- load("diploid_pinf_str_byregion_exceptD13locus_admix.RData")
sr <- get(str_data)

evno <- evanno(sr, plot = F)

qmat2 <- clumpp(sr, k = 2, sim.stat = "g.prime", repeats = 1000)
qmat3 <- clumpp(sr, k = 3, sim.stat = "g.prime", repeats = 1000)
qmat4 <- clumpp(sr, k = 4, sim.stat = "g.prime", repeats = 1000)
qmat5 <- clumpp(sr, k = 5, sim.stat = "g.prime", repeats = 1000)
# qmat6 <- clumpp(sr, k = 6, sim.stat = "g.prime", repeats = 1000)

#qmat_list <- list(qmat2, qmat3, qmat4, qmat5, qmat6)
qmat_list <- list(qmat2, qmat3, qmat4, qmat5)

edited_qmat_list <- qmat_list

for (i in 1:length(edited_qmat_list)){
  temp_mat <- edited_qmat_list[[i]]
  
  # temp_mat$orig.pop[temp_mat$orig.pop == ""] <- "CHA"
  
  key <- c("Michoacan" = "MICHO", "Chapingo" = "CHA", "Toluca" = "TOLU", "San Gerónimo" = "SG", "Juchitepec" = "JFH", "Tlaxcala" = "TLAX")
  
  temp_mat$orig.pop <- factor(key[temp_mat$orig.pop], ordered = TRUE, levels = key)
  
  edited_qmat_list[[i]] <- temp_mat
  
  
} 


# for (k in 1:length(edited_qmat_list)){
#   temp <- edited_qmat_list[[k]]
#   temp$orig.pop <- factor(temp$orig.pop, levels = unique(temp$orig.pop)[c(9,11,4,1,6,2,7,3,8,5,10)], ordered = TRUE)
#   edited_qmat_list[[k]] <- temp
# 
# }

for (k in 1:length(edited_qmat_list)){
  temp <- edited_qmat_list[[k]]
  temp$orig.pop <- factor(temp$orig.pop, levels = unique(temp$orig.pop)[c(6,1,4,3,2,5)], ordered = TRUE)
  edited_qmat_list[[k]] <- temp
  
}

plots <- lapply(edited_qmat_list, structurePlot, horiz = FALSE)
new_plots <- plots


for (k in 1:length(plots)){
 temp <- plots[[k]] +  
   theme(axis.text = element_text(size = 10, face = "bold", family = "Microsoft Sans Serif", colour = "black")) +
    theme(axis.title = element_text(size = 10, face = "bold", family = "Microsoft Sans Serif", colour = "black")) +
    theme(text = element_text(size = 10, face = "bold", family = "Microsoft Sans Serif", colour = "black")) 
   
 new_plots[[k]] <- temp

}

library(cowplot)
plot_grid(plotlist = new_plots, nrow = 4, ncol = 1, hjust = 1) +
  # theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  theme(panel.border = element_rect(colour = "blue", fill=NA, size=3))
+
theme(plot.margin=unit(c(0,0,0,0),"mm"))

ggsave("str_fig4.tiff", plot = last_plot(), width = 7, height = 9, dpi = 600, units = "in")

```


## Discriminant Analysis of Principal Components

```{r}

# set.seed(999)
# P.infx <- xvalDapc(tab(diploid_pinf, NA.method = "mean"), pop(diploid_pinf))

set.seed(999)
P.infx <- xvalDapc(tab(diploid_pinf, NA.method = "mean"), pop(diploid_pinf),
                   n.pca = 60:70,  n.rep = 100, 
                   parallel = "multicore", ncpus = 4L)


library(RColorBrewer)

myCol <- brewer.pal(nPop(diploid_pinf), "Dark2") %>% setNames(popNames(diploid_pinf))

# 
# tiff("dapc1.tiff", width = 7.2, height = 4, units = "in", res = 600, family = "Microsoft Sans Serif")
# par(mfrow = c(1,2))
# 
# scatter.dapc(P.infx$DAPC, col=myCol, clabel = 0.75, pch=15:19, scree.pca = TRUE, scree.da = FALSE, 
#         posi.pca = "topright", posi.leg = "topright", legend = F, 
#         cleg = 0.9, inset.solid = 1, xax = 1, yax = 2, cex.lab = 1, cex = 1, solid = 1, cstar = 0)
# 
# 
# 
# diploid_pinf_no_MCH <- popsub(diploid_pinf, blacklist = "Michoacan")
# 
# set.seed(999)
# P.infx1 <- xvalDapc(tab(diploid_pinf_no_MCH, NA.method = "mean"), pop(diploid_pinf_no_MCH),
#                    n.pca = 60:70,  n.rep = 100, 
#                    parallel = "multicore", ncpus = 4L)
# 
# scatter.dapc(P.infx1$DAPC, col=myCol, clabel = 0.75, pch=15:19, scree.pca = TRUE, scree.da = FALSE, 
#         posi.pca = "topright", posi.leg = "topright", legend = F, 
#         cleg = 0.9, inset.solid = 1, xax = 1, yax = 2, cex.lab = 1, cex = 1, solid = 1, cstar = 0)
# 
# dev.off()


############
source("scatterdapc.R")
tiff("Fig5.tiff", width = 7.2, height = 4, units = "in", res = 600, family = "Microsoft Sans Serif")
par(mfrow = c(1,2))
par(mar = c(1,1,1,3))


scatterdapc(P.infx$DAPC, col=myCol, clabel = 0.75, pch=15:19, scree.pca = TRUE, scree.da = FALSE, 
        posi.pca = "topright", posi.leg = "topright", legend = F, 
        cleg = 0.9, inset.solid = 1, xax = 1, yax = 2, cex.lab = 1, cex = 1, solid = 1, cstar = 0)
title(main = "A", col = "black", font.main = 2, adj = 0, line = -1)

scatterdapc(P.infx1$DAPC, col=myCol, clabel = 0.75, pch=15:19, scree.pca = TRUE, scree.da = FALSE, 
        posi.pca = "topright", posi.leg = "topright", legend = F, 
        cleg = 0.9, inset.solid = 1, xax = 1, yax = 2, cex.lab = 1, cex = 1, solid = 1, cstar = 0)
title(main = "B", col = "black", font.main =2, adj = 0, line = -1)

dev.off()










```



## Analysis of molecular variance
```{r}

repeat_length <- c(2, 2, 2, 3, 3, 2, 2, 2, 2, 2, 2)
bruvodist <- bruvo.dist(clonecorrect(diploid_pinf), replen = repeat_length)

amv <- poppr.amova(diploid_pinf, 
                   hier = ~Region, 
                   clonecorrect = TRUE, 
                   dist = bruvodist,
                   within = F)


myamv <- amv$results
myamv <- cbind(myamv, amv$componentsofcovariance$`%`)
ncol(myamv)
colnames(myamv) <- c("df", "SS", "MSS", "% variance")

knitr::kable(myamv, digits = 2,
             caption = "Table xxx. Analysis of Molecular Variance for clone corrected diploid P. infestans based on Bruvo’s distance ")


```


## Pairwise FST test
```{r}

diploid_pinf_cc <- clonecorrect(diploid_pinf)

library(strataG)
gen2gtype <- function (x) {
  
  gen.mat <- genind2df(x, usepop = TRUE, oneColPerAll = TRUE)
  strata <- x@strata
  rownames(strata) <- rownames(gen.mat)
  x@strata <- strata
  gen.mat[gen.mat == "NA"] <- NA
  has.pop <- !is.null(x@pop)
  df2gtypes(x = gen.mat, ploidy = x@ploidy[1], id.col = NULL, 
            strata.col = if (has.pop) 
              1
            else NULL, loc.col = if (has.pop) 
              2
            else 1, 
            schemes = x@strata,  other = other(x))
}

diploid_pinf_cc.g <- gen2gtype(diploid_pinf_cc)

pairwise_fst <- pairwiseTest(diploid_pinf_cc.g, stats = "fst", nrep = 10000)

fst_mat <- pairwise_fst$pair.mat$Fst
fst_mat[upper.tri(fst_mat)] <- t(fst_mat)[upper.tri(fst_mat)]
fst_mat[is.na(fst_mat)] <- 0

new_fst_mat <- fst_mat
#saveRDS(new_fst_mat, "new_fst_mat.RData", compress = F)
plot(ape::nj(as.dist(new_fst_mat)), type = "unrooted", edge.width = 2, rotate.tree = 240)
add.scale.bar()

plot(ape::nj(as.dist(new_fst_mat)), type = "phylogram")
add.scale.bar()

plot(nj(dist(new_fst_mat)))
#heatmap(new_fst_mat)
plot(hclust(dist(new_fst_mat)))


library(reshape2)
fst_mat[upper.tri(fst_mat)] <- NA
lower_tri <- melt(fst_mat, na.rm = TRUE)

library(ggplot2)
ggheatmap <- ggplot(lower_tri, aes(x = Var1, y = Var2, fill = value)) + geom_tile(color = "white") + 
  scale_fill_gradient(low = "green", high = "red" , space = "Lab", name="Pairwise FST") + theme_minimal() + 
   theme(axis.text.x = element_text(angle = 90, vjust = 1, size = 12, hjust = 1)) + coord_fixed() +
  labs(x = "Population", y = "Population") +
  theme(axis.text.y = element_text(size = 12)) +
  theme(axis.title = element_text(size = 12)) +
  geom_text(aes(label = round(value, 2)))

ggheatmap


kable(fst_mat, digits = 2,
      caption = "Table xx. Pairwise FST values (lower triangle) for diploid P.infestans genotypes from regions of Mexico using eleven SSR markers. Upper triangle represents the associated P-value for pairwise comparisons based on 10,000 permutation replicates.")


```


## Number of clusters based on BIC
```{r}
#library(adegenet)

## DETECTION WITH BIC (clear result)
foo.BIC <- find.clusters(diploid_pinf, n.pca=100, choose=FALSE)
plot(foo.BIC$Kstat[1:10], type="o", xlab="number of clusters (K)", ylab="BIC",
col="blue", main="Detection based on BIC")


points(4, foo.BIC$Kstat[4], pch="x", cex=3)
mtext(3, tex="'X' indicates the actual number of clusters")

## DETECTION WITH AIC (less clear-cut)
foo.AIC <- find.clusters(diploid_pinf, n.pca=100, choose=FALSE, stat="AIC")
plot(foo.AIC$Kstat[1:10], type="o", xlab="number of clusters (K)",
ylab="AIC", col="purple", main="Detection based on AIC")
points(2, foo.AIC$Kstat[2], pch="x", cex=3)
mtext(3, tex="'X' indicates the actual number of clusters")


# ## DETECTION WITH WSS (less clear-cut)
# foo.WSS <- find.clusters(diploid_pinf, n.pca=100, choose=FALSE, stat="WSS")
# plot(foo.WSS$Kstat[1:10], type="o", xlab="number of clusters (K)", ylab="WSS
# (residual variance)", col="red", main="Detection based on WSS")
# points(2, foo.WSS$Kstat[2], pch="x", cex=3)
# mtext(3, tex="'X' indicates the actual number of clusters")



test <- find.clusters(, n.pca = 100, 
              stat = "BIC", choose.n.clust = F, criterion = "diffNgroup", max.n.clust = 10)


```


```{r, eval=FALSE, include=FALSE}


## Inbreeding coefficient : 
### Measure of deviation from HWE. Measures differences in observed and expected heterozugosity, standardized by expected heterozygosity. FIS = 0 meaning pop is in HWE.

library(hierfstat)
source("FIS.R")

fis(diploid_pinf)

```


## Isolation by distance
```{r}

lat_lon <- read.csv("Dgeo_MX.csv")
colnames(lat_lon) <- c("name", "lat", "lon")
source("GeoDistanceInMetresMatrix.R")

geodist_mat <- GeoDistanceInMetresMatrix(lat_lon) / 1000
geodist_mat <- as.dist(geodist_mat)


new_fst_mat <- readRDS("new_fst_mat.RData")
fstdist_mat <- as.dist(new_fst_mat)

ibd <- mantel.randtest(fstdist_mat, geodist_mat, nrepet = 999)
plot(ibd, main = "Mantel's test")
ibd

# library(MASS)
# dens <- kde2d(geodist_mat, fstdist_mat, n=300)
# myPal <- colorRampPalette(c("white","blue","gold", "orange", "red"))
# plot(geodist_mat, fstdist_mat, pch=20,cex=.5)
# image(dens, col=transp(myPal(300),.7), add=TRUE)
# abline(lm(fstdist_mat~geodist_mat))
# title("Isolation by distance plot")


tiff("Fig6.tiff", width = 7, height = 7, units = "in", res = 600, pointsize = 10)
plot(geodist_mat, fstdist_mat, xlab = "Geographical distance (km)", ylab = "Genetic distance (FST)",
     pch = 19, bg = "black", cex.lab = 1.5, cex.axis = 1.5, font.lab = 2, 
           font = 2, family = "Microsoft Sans Serif")
abline(lm(fstdist_mat~geodist_mat))

#tiff("Fig6.tiff", width = 7, height = 7, units = "in", res = 600, pointsize = 10)
dev.off()



summary(lm(fstdist_mat~geodist_mat))

##positive corelation but not significant enough. This explains partially the population structure.


par(pin = c(3.5, 3.5))


tiff("Fig6.tiff", width = 7, height = 7, units = "in", res = 600)
plot(geodist_mat, fstdist_mat, xlab = "Geographical distance (km)", ylab = "Genetic distance (FST)",
     pch = 19, bg = "black", font.lab = 2, 
           font = 2, family = "Microsoft Sans Serif")
abline(lm(fstdist_mat~geodist_mat))


```


```{r, eval=FALSE, include=FALSE}

library(reshape2)
library(dplyr)
library(tidyr)


diversity <- diversity_ci(diploid_pinf, n = 100L)
CI <- melt(diversity[[3]]) %>% spread(CI, value) %>% rename(lb = `2.5 %`, ub = `97.5 %`)
obs <- melt(diversity[[1]]) %>% rename(observed = value)


dat <- merge(CI, obs)

sim_div <- filter(dat, Index == "lambda")

sim_div$Pop<- factor(sim_div$Pop, levels = sim_div$Pop[c(3,1,6,2,4,5,7)])

ggplot(sim_div, aes(x = Pop, y = observed, color = Pop)) +
geom_point(size = 5) +
   geom_errorbar(aes(ymax = ub, ymin = lb), lwd = 1.25) +
   theme(axis.text.x = element_text(hjust = 1, vjust = 0.5, angle = 60, size = 15)) +
   theme(text = element_text(size = rel(5))) +
   labs(title = "Simpson's diversity index") +
   theme(plot.title = element_text(size = 35)) +
    theme(legend.position = "none") +
   labs(x = "Population", y = "Observed value")



```





```{r, eval=FALSE, include=FALSE}

## allelic richness

# library(strataG)
# diploid_pinf.gtypes <- genind2gtypes(clonecorrect(diploid_pinf))
# allelicRichness(diploid_pinf.gtypes)
# summarizeLoci(diploid_pinf.gtypes)

library(PopGenReport)
allleic_rich <- allel.rich(diploid_pinf)

allelic_richness <- allleic_rich$all.richness
allelic_richness <- as.data.frame(apply(allelic_richness, MARGIN = 2, mean))
colnames(allelic_richness) <- "Allelic richness"


sum_richness.df <- as.data.frame(allleic_rich$sum.richness)
colnames(sum_richness.df) <- "Sum richness"

allelic_summary <- cbind(allelic_richness, sum_richness.df)
pri_alleles <- private_alleles(diploid_pinf)
rowSums(pri_alleles > 0 )

library(ggplot2)
ggplot(allelic_summary, aes(rownames(allelic_summary), allelic_summary$`Sum richness`)) + geom_bar(stat = "identity") 





```



```{r}


diploid_pinf_genpop <- genind2genpop(diploid_pinf)
save(diploid_pinf_genpop, file = "diploid_pinf.gen")

library(diveRsity)

divMigrate("diploid_pinf.gen", stat ="d_jost")


divMigrate("diploid_pinf_genpop.gen", stat ="d_jost")


data(Test_data)


Test_data

divMigrate(infile = t(df), stat = "d_jost", plot_network = T)


df <- genind2df(diploid_pinf)

```


```{r}


## ggtree
source("https://bioconductor.org/biocLite.R")
biocLite("ggtree", type = "source")

library(ggtree)
library(ggrepel)


repeat_length <- c(2, 2, 2, 3, 3, 2, 2, 2, 2, 2, 2)

diploid_pinf <- clonecorrect(diploid_pinf)
tree_nj <- bruvo.boot(diploid_pinf, replen = repeat_length, 
                   sample = 1000, cutoff = 70, tree = "nj")

tree_nj <- readRDS("tree_nj.RData")
tree_nj$node.labels[tree_nj$node.labels > 70]  <- "*" 

mycol <- rainbow(6)
mycol[2] <- "#000000"
mycol <- mycol %>% setNames(popNames(diploid_pinf))

x <- apeBoot(tree_nj, tree_nj$node.label)
strata <- dplyr::data_frame(taxa = indNames(diploid_pinf)) %>% cbind(strata(diploid_pinf)) 
#tree_nj$tip.label <- as.character(strata$Region) 
# 
# plot(tree_nj,
#             tip.color = mycol, show.node.label = TRUE, use.edge.length = F,
#             edge.width = 2,
#             align.tip.label = T,
#             font = 2, adj = 1, label.offset = 1,
#             main = "NJ tree.", cex = 0.65, node.pos = 1, type = "unrooted")


test_tree <- ggtree(x, layout = "circular", branch.length = "none") +
  geom_text(aes(label = bootstrap), color = "red")
  
  
final_tree <- test_tree %<+% strata +
              geom_tippoint(aes(color = Region), alpha = 1, size = 1) +
              scale_color_manual(values = mycol) +
              theme(legend.text = element_text(size = 10)) +
              theme(legend.position = "right") + 
              theme(text = element_text(size =10, face = "bold", family = "Microsoft Sans Serif", colour = "black"))
  


ggsave("NJ.tiff", plot = last_plot(), width = 7, height = 7, dpi = 600, units = "in")


# test_tree <- ggtree(x, layout = "circular", branch.length = "none") +
#   ggtitle("NJ tree") +
#   geom_label_repel(aes(label = bootstrap, size = bootstrap),
#   nudge_x = -0.015, nudge_y = -0.005) +
#   scale_size(range = c(2, 4)) +
#   
#   theme(plot.title = element_text(size = 30))



tree_nj


g1 = as(tree_nj, 'phylo4') 

d = data.frame(color=sample(c('red', 'blue', 'green'), 860, replace=T)) 

rownames(d) = tree_nj$tip.label 

g2 = phylo4d(g1, d) 

rNodeData <- data.frame(randomTrait = rnorm(nNodes(g1)), color = sample(c('purple', 'yellow', 'black'), nNodes(g1), replace=T), row.names = nodeId(g1, "internal")) 


nodeData(g2) <- rNodeData 





min_span_net <- bruvo.msn(diploid_pinf_cc, replen = repeat_length, 
                          add = TRUE, loss = F, showplot = FALSE, 
                          include.ties = FALSE)


set.seed(99)
plot_poppr_msn(diploid_pinf_cc,
               min_span_net,
               inds = "F",
               mlg = FALSE,
               gadj = 3,
               nodebase = 1.15,
               palette = mycol,
               cutoff = NULL,
               quantiles = FALSE,
               beforecut = TRUE)


tree_nj











```






